\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}

\bibitem{t01}
	 J.Buck and E.Buck (1978), Toward a functional interpretation of synchronous ashing by fireflies, The American Naturalist, 112(985):471-492.
	\bibitem{t02}
	J. Yuan, Z.-H. Zhou, H. Mu, Y.-T. Sun, and L. Li, Formation control
 of autonomous underwater vehicles based on finite-time consensus algorithms,
	in Proceedings of Chinese Intelligent Automation Conference,
	pp.1-8, Springer, 2013.
	
	\bibitem{t03}
	M. Davoodi, N. Meskin, and K. Khorasani,Simultaneous fault detection and control design for a network of multi-agent systems, in European Control Conference, pp. 575-581, June 2014.
	
	\bibitem{t04}
	 Z. Gallehdari, N. Meskin, and K. Khorasani, Cost performance based control reconfiguration in multi-agent systems, in American Control
	 Conference,pp. 509-516, IEEE, 2014.
	
	\bibitem{t05}
	 O. Saif, I. Fantoni, and A. Zavala-Rio,Flocking of multiple unmanned aerial vehicles by lqr control, in International Conference on Unmanned Aircraft Systems, pp.222-228, IEEE, 2014.
	
	\bibitem{t06}
    Y. F. Chen, N. K. Ure, G. Chowdhary, J. P. How, and J. Vian, Planning for large-scale multi-agent problems via hierarchical decomposition with applications to UAV health management, in American Control Conference,pp.1279-1285 IEEE, 2014.
	
	\bibitem{t07}
	J. Leonard, A. Savvaris, and A. Tsourdos, Energy management in swarm of unmanned aerial vehicles,Journal of Intelligent  Robotic Systems, vol. 74, no. 1-2, pp.233-250, 2014.
	
	\bibitem{t08}
    A.Souliman, A. Joukhadar, H.Alturbeh, and J. F.Whidborne, Intelligent collision avoidance for multi agent mobile robots, in Intelligent Systems for Science and Information, pp.297-315, Springer, 2014.
	
	\bibitem{t09}
   S. Z. Khong, Y. Tan, C. Manzie, and D. Nesic, Multi-agent source seeking via discrete-time extremum seeking control,Automatica, 2014.
	
	\bibitem{t10}
   M. Guo, M. M. Zavlanos, and D. V. Dimarogonas, Controlling the relative agent motion in multi-agent formation stabilization, IEEE Transaction on Automatic Control, 2014.
	
	\bibitem{t11}
  P. Lin, W. Lu, and Y. Song, Distributed nested rotating consensus problem of multi-agent systems, in The 26th Chinese Control and Decision Conference, pp. 1785-1789, IEEE,2014.
	
	\bibitem{t12}
   G.Wen, Z. Duan, W. Ren, and G. Chen, Distributed consensus of multi-agent systems with general linear node dynamics and intermittent communications, International Journal of Robust and Nonlinear Control, 2013.
	
	\bibitem{t13}
	A. Ryan, M. Zennaro, A. Howell, R. Sengupta, and J. K. Hedrick,An overview of emerging results in cooperative uav control, in Proceedings of the 43rd IEEE Conference on Decision and Control, pp. 602-607,2004.
	
	\bibitem{t14}
   R. Olfati-Saber, J. A. Fax, and R. M. Murray,Consensus and cooperation in networked multi-agent systems, Proceedings of the IEEE, vol. 95,no. 1, pp.215-233, 2007.
	\bibitem{t15}
	W. Ren, R. Beard, and E. Atkins,A survey of consensus problems in multi-agent coordination, in Proceedings of the American Control Conference, pp. 1859-1864 vol. 3, June 2005.
	\bibitem{t16}
	S. Feng and H. Zhang,Formation control for wheeled mobile robots based on consensus protocol, in IEEE International Conference on Information
	and Automation, pp. 696-700, june 2011.
	\bibitem{t17}
	E. Semsar-Kazerooni and K. Khorasani, Team consensus for a network of unmanned vehicles in presence of actuator faults, IEEE Transactions on Control Systems Technology, vol. 18, no. 5, pp. 1155-1161, 2010.
	\bibitem{t18}
	S. M. Azizi and K. Khorasani, Cooperative actuator fault accommodation of formation flying vehicles with absolute measurements, in 49th IEEE Conference on Decision and Control, pp. 6299-6304,2010.
	\bibitem{t19}
	M. Joordens and M. Jamshidi, Consensus control for a system of underwater swarm robots,IEEE Systems Journal, vol. 4, pp. 65-73, March 2010. 
	\bibitem{t20}
	J. liang Peng, X. xia Sun, F. Zhu, and X. qing Li, Multi uavs cooperative task assignment using multi agent, in Chinese Control and Decision
	Conference, pp. 4517-4520, july 2008.
	\bibitem{t21}
	B. He and J. Wen, Cooperative load transport: A formation-control perspective, IEEE Transactions on Robotics, vol. 26, pp. 742-750, aug.2010.
	\bibitem{t22}
	D. Xu and K. Xia,Role assignment, non-communicative multi-agent coordination in dynamic environments based on the situation calculus, in WRI Global Congress on Intelligent Systems, vol. 1, pp. 89-93, may
	2009.
	\bibitem{t23}
	I. de Oliveira, F. Carvalho, J. B. Camargo, and L. M. Sato,Multi-agent tools for air traffic management, in 11th IEEE International Conference on Computational Science and Engineering Workshops, pp. 355-360, july 2008.
	\bibitem{t24}
	W. Ren and R. W. Beard, Distributed Consensus in Multi-vehicle Cooperative Control; Theory and Applications. Springer, 2008.
%	\bibitem{t25}
%	R. Olfati-saber and R. M. Murray, “Distributed cooperative control
%	of multiple vehicle formations using structural potential functions,” in
%	IFAC World Congress, 2002.
%	\bibitem{t26}
%	W. Ren, R. Beard, and E. Atkins, “Information consensus in multivehicle
%	cooperative control,” IEEE Control Systems, vol. 27, no. 2, pp. 71–82,
%	2007.
%	\bibitem{t27}
%	D. Smallwood and L. Whitcomb, “Model-based dynamic positioning of
%	underwater robotic vehicles: theory and experiment,” IEEE Journal of
%	Oceanic Engineering, vol. 29, no. 1, pp. 169–186, 2004.
%	\bibitem{t28}
%	R. Olfati-Saber and J. Shamma, “Consensus filters for sensor networks
%	and distributed sensor fusion,” in 44th IEEE Conference on Decision
%	and Control and European Control Conference, pp. 6698–6703, 2005.
%	\bibitem{t29}
%	U. Munz, A. Papachristodoulou, and F. Allgwer, “Consensus in multiagent
%	systems with coupling delays and switching topology,” IEEE
%	Transactions on Automatic Control, vol. 26, pp. 2976–2982, December
%	2011.
%	\bibitem{t30}
%	A. Seuret, D. V. Dimarogonas, and K. H. Johansson, “Consensus under
%	communication delays,” in 47th IEEE Conference on Decision and
%	Control, (Cancun, Mexico), pp. 4922–4927, December 2008.
%	\bibitem{t31}
%	A. Ajorlou, A. Momeni, and A. G. Aghdam, “A class of bounded distributed
%	control strategies for connectivity preservation in multi-agent
%	systems,” IEEE Trans. on Automatic Control, vol. 55, no. 12, pp. 2828–
%	2833, 2010.
	\bibitem{t25}
   Ho Hou, Z.-G., Cheng, L., Tan, M.: Decentralized robust adaptive control for the multi-agent system consensus problem using neural networks, IEEE Trans. Syst.Man Cybern. B, Cybern., 2009, 39, (3), pp. 636-647.
	\bibitem{t26}
	 R.Lu,W.yu,J.Lu,X.ue, A Synchronization on complex networks of networks, IEEE Trans. Neural Netw. Learn. Syst., 2014, PP, (99), pp. 1-1.
	\bibitem{t27}
	W.Ren,E.Atkins, Distributed multi-vehicle coordinated control via local information exchange, Int. J. Robust Nonlinear Control, 2007, 17, (10-11),pp. 1002-1033.
	\bibitem{t28}
	Y.Hong, G.Chen, L.Bushnell, Distributed observers design for leader followingcontrol of multi-agent networks, Automatica, 2008, 44, (3), pp. 846-850.
    \bibitem{t29}
     J.Hu, Y.Hong ,Leader following coordination of multi-agent systems with coupling time delays, Phys. A, Stat. Mech. Appl., 2007, 374, (2), pp. 853-863.
    \bibitem{t30}
    A. Jadbabaie, J. Lin, and S. M. Morse, Coordination of groups of mobile autonomous agents using nearest neighbour rules, IEEE Trans. Autom.Control, vol. 48, no. 6, pp. 988-1001, 2003.
    
    \bibitem{t31}
     R. Olfati-Saber, J. Fax and R. Murray, Consensus and cooperation in networked multi-agent systems, Proceedings of IEEE, vol. 95, no. 1, pp.
     215-233, 2007.
    
     
     \bibitem{c19}R.Varga, Gersgorin and his circles, Berlin: Springer, 2004.
     
     
     \bibitem{c19} C. Ren and C. L. P. Chen, "Sliding mode leader-following consensus controllers for second-order non-linear multi-agent systems," in IET Control Theory $\&$ Applications, vol. 9, no. 10, pp. 1544-1552, 2015.
     
     
    \bibitem{c20} L. Rosier, "Homogeneous Lyapunov function for homogeneous continuous vector field", Systems $\&$ Control Letters, vol. 19, no. 6, pp. 467-473, 1992. Available: 10.1016/0167-6911(92)90078-7 [Accessed 30 May 2019].
     \bibitem{c21}
    K. Patel and A. Mehta, "Discrete-time Sliding Mode Control for Leader Following Discrete-time Multi-Agent System," IECON 2018 - 44th Annual Conference of the IEEE Industrial Electronics Society, Washington, DC, 2018, pp. 2288-2292.
    \bibitem{c22}
    S. Chakrabarty, B. Bandyopadhyay, and A. Bartoszewicz, ``Discretetime
    sliding mode control with outputs of relative degree more
    than one", in Recent Developments in Sliding Mode Control
    Theory and Applications. InTech, Jun. 2017. [Online]. Available:
    https://doi.org/10.5772/intechopen.68931
    \bibitem{c23}
    I. Salgado, S. Kamal, B. Bandyopadhyay, I. Chairez, and
    L. Fridman, “Control of discrete time systems based on
    recurrent super-twisting-like algorithm,” ISA Transactions, vol. 64,
    DOI https://doi.org/10.1016/j.isatra.2016.04.024, pp. 47 – 55, 2016.
    [Online]. Available: http://www.sciencedirect.com/science/article/pii/
    S0019057816300702
    
%     \bibitem{c20}D.Naidu, Optimal control systems,Boca Raton, Fla: CRC Press, 2003.
%     \bibitem{c21} W.Gao,Y. Wang, and A.Homaifa, Discrete-Time Variable Structure Control Systems,IEEE Transaction on Industrial Electronics,Vol.42,No.2,April 1995.
     %\bibitem{c17}Ya-Kun Zhu, Xin-Ping Guan, Xiao-Yuan Luo. Finite-time Consensus for Multi-agent Systems via Nonlinear Control Protocols,International Journal of Automation and Computing,October 2013, 455-462.
     
     
     
     
     
     
     
     
     %\bibitem{c18} C. Ren, C.L.P.Chen. Sliding mode leader-following consensus
     %controllers for second-order non-linear multi-agent systems,IET Control Theory and Applications December 2014,Vol. 9, Iss. 10, pp. 1544–1552.
     %\bibitem{ad1} A.sinha, R.kumar Mishra,Consensus tracking in multi agent system with
     %nonlinear and non identical dynamics via event driven sliding modes,preprint IEEE Transactions on Automatic Control 5 dec 2017.
     %\bibitem{ad2}Y. Pan, H. Werner, Z. Huang and M. Bartels, "Distributed cooperative control of leader–follower multi-agent systems under packet dropouts for quadcopters", 2018.
     %
     %\bibitem{c19} Z. Li, Z. Duan, G. Chen, and L. Huang, Consensus of multiagent
     %systems and synchronization of complex networks: A unified viewpoint,IEEE Trans. Circuits Syst. I, Reg. Papers, vol. 57, no. 1, pp. 213–224,
     %Jan. 2010.
     %\bibitem{c20} K. Hengster-Movric, K. You, F. L. Lewis, and L. Xie, Synchronization
     %of discrete-time multi-agent systems on graphs using Riccati design,
     %Automatica, vol. 49, no. 2, pp. 414–423, 2013.
     %\bibitem{c21} Z. Li, Z. Duan, and G. Chen, Consensus of discrete-time linear
     %multi-agent systems with observer-type protocols, Discrete Continuous
     %Dyn. Syst., B, vol. 16, no. 2, pp. 489–505, 2011.
     %\bibitem{c22} W.Gao,Y. Wang, and A.Homaifa,Discrete-Time Variable Structure Control Systems,IEEE Transaction on Industrial Electronics,Vol.42,No.2,April 1995.
     %\bibitem{c23}H.Zhang,T.Feng,H.Liang, and Y. Luo,LQR-Based Optimal Distributed Cooperative Design for Linear Discrete-Time Multi agent Systems,IEEE Transactions On Neural Networks And Learning Systems,Vol.28,No.3,March 2017.
     %\bibitem{c24} Khoo, S., Xie, L., Man, Z.: Robust finite-time consensus tracking algorithm for multirobot systems, IEEE/ASME Trans. Mechatron., 2009, 14, (2), pp. 219–228.
\end{thebibliography}
